\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-05 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Sec. V

The network reduced admittance matrix $\bm{Y}\in\mathbb{C}^{n\times n}$ in \eqref{DefParam} is the Schur complement of \eqref{PartionedAdmittanceMatrix} w.r.t. the block $\bm{Y}_{\rm{int}}$, i.e.,
\[\bm{Y} = \bm{Y}_{\rm{unreduced}} / \bm{Y}_{\rm{int}} := \bm{Y}_{\rm{bnd}} - \bm{Y}_{\rm{bnd{\text{-}}int}} \bm{Y}_{\rm{int}}^{-1}\bm{Y}_{\rm{bnd{\text{-}}int}}^{\top}.\]

The network reduced current vector $I\in\mathbb{C}^{n}$ in \eqref{defPi} is obtained as
\[I  = \bm{Y}E_{\rm{bnd}} - I_{\rm{bnd}}.\]

>>>>

The network reduced admittance matrix $\bm{Y}\in\mathbb{C}^{n\times n}$ in \eqref{DefParam} is the Schur complement of \eqref{PartionedAdmittanceMatrix} w.r.t. the block $\bm{Y}_{\rm{int}}$, i.e.,
\[\bm{Y} = \bm{Y}_{\rm{unreduced}} / \bm{Y}_{\rm{int}} := \bm{Y}_{\rm{bnd}} - \bm{Y}_{\rm{bnd{\text{-}}int}} \bm{Y}_{\rm{int}}^{-1}\bm{Y}_{\rm{bnd{\text{-}}int}}^{\top}.\]
The network reduced current vector $I\in\mathbb{C}^{n}$ in \eqref{defPi} is obtained as
\[I  = \bm{Y}E_{\rm{bnd}} - I_{\rm{bnd}}.\]
